Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2022-09-23 RR_manuscript/Draft_RR.Rmd
♻️ - edit methods phase 1-3; change tense to past

In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
<!-- TODOLATER: include number of teams when known -->
Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study.
The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
The teams will be instructed to answer the following research question, using the provided data set: *Do speakers acoustically modify utterances to signal atypical word combinations?*

@@

As outlined in Section [Operationalizing speech](#s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.

In this study, we will follow the procedures proposed by @Parker2020 and @aczel2021.
The project involves the following five phases:

1. \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review others' data analyses.
2. \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
3. \textsc{Review}: We will ask reviewers to generate peer-review ratings of the analyses based on methods (not results).
4. \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
5. \textsc{Write-up}: We will collaboratively produce the final manuscript.

We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.

The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://bit.ly/3AqU1ul>.
The main repository holds three OSF components, `Data`, `Questionnaires`, and `Cache`, and it is linked to the GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).^["Questions" and "Join Project" buttons will be functioning when recruitment starts. "Join Project" will link to the intake form.]
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
Social media advertising will be accompanied by a short recruitment form (`recruitment_form.pdf`)
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (`analytic_approach_quest.pdf`).
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
Recruitment for this project will commence upon receiving in-principle acceptance.

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
The code is available at <https://many-speech-analyses.github.io/suppl/simulations.html>, Section 2.^[Cached model outputs can be found at <https://bit.ly/3AgdHAN>.]
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we will sample as many analysts as possible.
We have received initial expression of interest to participate from more than 200 analysts.

After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
Informed consent will be obtained as part of the intake form.

@@

The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (`intake_form.pdf`).
A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
To do so, they will be given the data generated by the experiment described in Section [The data set](#s:dataset).
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.

Once their analysis is complete, they will answer a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.

@@

Each analysis will be evaluated by four different analysts teams who function as peer-reviewers.
Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

The reviewers will also be given the option to include further comments in a text box for each of the three ratings.

After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.

>>>>

In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the *operationalization* of a complex signal and decisions regarding *statistical analysis*.
<!-- TODOLATER: include number of teams when known -->
Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
This is an important addition in that the increased number of "forking paths" in the "garden of analytic choices", deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.

@@

For the present study, 30 analysis teams have received access to the entire data set generated by the production study.
The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
The teams were instructed to answer the following research question, using the provided data set: *Do speakers acoustically modify utterances to signal atypical word combinations?*

@@

As outlined in Section [Operationalizing speech](#s:operspeech), researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.

In this study, we followed the procedures proposed by @Parker2020 and @aczel2021.
The project involved the following five phases:

1. \textsc{Recruitment}: We recruited independent groups of researchers to analyze the data and review others' data analyses.
2. \textsc{Team Analysis}: We gave researchers access to the speech corpus and let them analyze the data as they saw fit.
3. \textsc{Review}: We asked reviewers to generate peer-review ratings of the analyses based on methods (not results).
4. \textsc{Meta-analysis}: We evaluated variability among the different analyses and how different predictors affected the outcomes.
5. \textsc{Write-up}: We collaboratively produced the final manuscript.

We have initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would have taken nine months.
<!-- The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams. -->
Phase 4. (meta-analysis) took longer than initially thought and the total duration of the project ended up lasting 12 months.

The project OSF repository contains all the materials mentioned in this paper and can be accessed at <https://bit.ly/3AqU1ul>.
The repository holds three main OSF components (`Data`, `Teams analyses` and `Questionnaires`), and a link to the project's GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

An online landing page provided a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (<https://many-speech-analyses.github.io>).
The project was advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth. 
Social media advertising was accompanied by a short recruitment form (`recruitment_form.pdf`).
The target population comprised active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines. 
All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (`analytic_approach_quest.pdf`).
Researchers could choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.^[Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.]
Recruitment for this project commenced after having received in-principle acceptance.

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect *per se*.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from @silberzahn2018many.
The code is available at <https://many-speech-analyses.github.io/suppl/simulations.html>, Section 2.^[Cached model outputs can be found at <https://bit.ly/3AgdHAN>.]
Variability among teams was operationalized as the standard deviation of the teams' reported effects from @silberzahn2018many (which we *z*-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 *z*-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams. 
Thus in order to achieve our main goal, i.e. estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expression of interest to participate from more than 200 analysts, although there has been a substantial drop-out rate (see Section Results).

After submitting their analyses, we asked the analysts to also function as peer-reviewers.
Each team had to review four other analyses.
All analysts involved share co-authorship on this manuscript and participated in the collaborative process of producing the final manuscript.
Informed consent was obtained as part of the intake form.

@@

The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (`intake_form.pdf`).
A PDF version of this and all other questionnaires are available in the repository's `Questionnaires` component, at <https://bit.ly/3Cf3fdm>.
The questionnaire collected information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We then requested that they answer the question: *Do speakers acoustically modify utterances to signal atypical word combinations?*
To do so, they were given the data generated by the experiment described in Section [The data set](#s:dataset).
The data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the `Data` component at <https://bit.ly/3Ahawc7>.

Once their analysis was complete, they answered a structured questionnaire (`analytic_quest.pdf`), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They also uploaded their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.

@@

Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
Reviewers evaluated the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences was systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer was as follows.
First, the reviewer received a description of the methods of a single analysis.
This included the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
The reviewer was then asked in an online questionnaire (`peer_review_quest.pdf`) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they were given the following guidelines:

@@

The reviewers were also given the option to include further comments in a text box for each of the three ratings.

After submitting the review, a methods section from a second analysis was then made available to the reviewer.
This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.^[We initially planned to simultaneously present all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation. We have decided to skip this last step due to time constrains.]

### 2022-09-23 RR_manuscript/Draft_RR.tex
♻️ - edit methods phase 1-3; change tense to past

In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
Specifically, we discuss the degree of variability in research results obtained by N teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.

@@

For the present study, N analysis teams will receive access to the entire data set generated by the production study.
The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
The teams will be instructed to answer the following research question, using the provided data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}

@@

As outlined in Section \protect\hyperlink{s:operspeech}{Operationalizing speech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employ a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.

In this study, we will follow the procedures proposed by \citet{Parker2020} and \citet{aczel2021}.
The project involves the following five phases:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textsc{Recruitment}: We will recruit independent groups of researchers to analyze the data and review others' data analyses.
\item
  \textsc{Team Analysis}: We will give researchers access to the speech corpus and let them analyze the data as they see fit.
\item
  \textsc{Review}: We will ask reviewers to generate peer-review ratings of the analyses based on methods (not results).
\item
  \textsc{Meta-analysis}: We will evaluate variability among the different analyses and how different predictors affect the outcomes.
\item
  \textsc{Write-up}: We will collaboratively produce the final manuscript.
\end{enumerate}

We estimate that this process, from the time of an in-principle acceptance of this Stage 1 Registered Report to the end of Phase 5, will take nine months.
The factor most likely to delay our time-line is the rate of completion of the original set of analyses by independent analysis teams.

The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://bit.ly/3AqU1ul}.
The main repository holds three OSF components, \texttt{Data}, \texttt{Questionnaires}, and \texttt{Cache}, and it is linked to the GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

An online landing page will provide a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).\footnote{``Questions'' and ``Join Project'' buttons will be functioning when recruitment starts. ``Join Project'' will link to the intake form.}
The project will be advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
Social media advertising will be accompanied by a short recruitment form (\texttt{recruitment\_form.pdf})
The target population comprises active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
All individuals interested in participating will be asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
Researchers can choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
Recruitment for this project will commence upon receiving in-principle acceptance.

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
The code is available at \url{https://many-speech-analyses.github.io/suppl/simulations.html}, Section 2.\footnote{Cached model outputs can be found at \url{https://bit.ly/3AgdHAN}.}
Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
Thus in order to achieve our main goal, i.e.~estimating variability among teams, we consider a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we will sample as many analysts as possible.
We have received initial expression of interest to participate from more than 200 analysts.

After submitting their analyses, we will ask analysts to also function as peer-reviewers. Each team must review four other analyses.
All analysts will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
Informed consent will be obtained as part of the intake form.

@@

The analysis teams will register for participation and each of the analysts individually will answer a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
The questionnaire collects information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We will then request that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they will be given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
The data will include the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.

Once their analysis is complete, they will answer a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They will also upload their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.

@@

Each analysis will be evaluated by four different analysts teams who function as peer-reviewers.
Each peer-reviewer will be randomly assigned to analyses from at least four analysis teams.
Reviewers will evaluate the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences will be systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer will be as follows.
First, the reviewer will receive a description of the methods of a single analysis.
This will include the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
The reviewer will then be asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they will be given the following guidelines:

@@

The reviewers will also be given the option to include further comments in a text box for each of the three ratings.

After submitting the review, a methods section from a second analysis will then be made available to the reviewer.
This same sequence will be followed until all analyses allocated to a given reviewer have been provided and reviewed.
After providing the final review, the reviewer will be simultaneously presented with all four (or more) methods sections that the reviewer has just completed reviewing, the option to revise their original ratings, and a text box to provide an explanation.

>>>>

In this article, we investigate the impact of analytic choices on research results when many analyst teams analyze the same speech production data set, a process that involves both decisions regarding the \emph{operationalization} of a complex signal and decisions regarding \emph{statistical analysis}.
Specifically, we discuss the degree of variability in research results obtained by 30 teams who had to choose the operationalisation and statistical procedures to answer the same research question, on the basis of the same set of raw data (here, speech recordings).
Our goals are twofold: (i) our study conceptually replicates previous many-analyses projects, by probing the effects of different statistical analyses and by assessing the generalizability of published findings to other disciplines (here, the speech sciences);
(ii) our study extends the scope of inquiry to include flexibility in the operationalisation of complex human behavior (here, human speech).
This is an important addition in that the increased number of ``forking paths'' in the ``garden of analytic choices'', deriving from the many decisions involved in quantification, might reveal a higher degree of variability across analysts than what previously observed, thus giving us a more realistic estimate of variability across analysts.

@@

For the present study, 30 analysis teams have received access to the entire data set generated by the production study.
The data set is constituted by audio recordings and annotation files in a format that is typical for the field.
The teams were instructed to answer the following research question, using the provided data set: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}

@@

As outlined in Section \protect\hyperlink{s:operspeech}{Operationalizing speech}, researchers are faced with a large amount of analytic choices when analyzing a multidimensional signal such as speech.
Analysts must identify and operationalize relevant measurements, as well as the temporal domain(s) from which these measurements are to be taken, and then possibly transform said measurements before submitting them to statistical models, which must be chosen alongside inferential criteria.
The complexity of speech data constitutes the ideal testing ground to assess the upper bound of analytic flexibility that social science might face across disciplines.
We will employed a meta-analytic approach to assess (i) the variability of the reported effects, and (ii) how analytic and researcher-related predictors affect the final results.

In this study, we followed the procedures proposed by \citet{Parker2020} and \citet{aczel2021}.
The project involved the following five phases:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  \textsc{Recruitment}: We recruited independent groups of researchers to analyze the data and review others' data analyses.
\item
  \textsc{Team Analysis}: We gave researchers access to the speech corpus and let them analyze the data as they saw fit.
\item
  \textsc{Review}: We asked reviewers to generate peer-review ratings of the analyses based on methods (not results).
\item
  \textsc{Meta-analysis}: We evaluated variability among the different analyses and how different predictors affected the outcomes.
\item
  \textsc{Write-up}: We collaboratively produced the final manuscript.
\end{enumerate}

We have initially estimated that this process, from the time of an in-principle acceptance of the Stage 1 Registered Report to the end of Phase 5, would have taken nine months.
Phase 4. (meta-analysis) took longer than initially thought and the total duration of the project ended up lasting 12 months.

The project OSF repository contains all the materials mentioned in this paper and can be accessed at \url{https://bit.ly/3AqU1ul}.
The repository holds three main OSF components (\texttt{Data}, \texttt{Teams\ analyses} and \texttt{Questionnaires}), and a link to the project's GitHub repository.
The following sections report the criteria for sample size, data exclusions, data manipulations, and all the measures in the study.

@@

An online landing page provided a general description of the project, including a short pre-recorded slide-show that summarizes the data set and research question (\url{https://many-speech-analyses.github.io}).
The project was advertised via social media, using mailing lists for linguistic and psychological societies, and via word of mouth.
Social media advertising was accompanied by a short recruitment form (\texttt{recruitment\_form.pdf}).
The target population comprised active speech science researchers with a graduate/doctoral degree (or currently studying for a graduate/doctoral degree) in relevant disciplines.
All individuals interested in participating were asked to complete a questionnaire detailing their familiarity with numerous analytical approaches common in the speech sciences (\texttt{analytic\_approach\_quest.pdf}).
Researchers could choose to work independently or in a small team.
For the sake of simplicity, we will refer both to a single researcher and teams as \textsc{analysis teams}.\footnote{Terms in small caps in this and later sections are included with their definition in the glossary at the end of the paper for the reader's convenience.}
Recruitment for this project commenced after having received in-principle acceptance.

As outlined above, our primary aim is to assess the variability of the reported effects, rather than the meta-analytic estimate of the investigated effect \emph{per se}.
To estimate the degree of uncertainty around effect variability as driven by number of teams, we ran a series of sample size simulations with values of variability extracted from \citet{silberzahn2018many}.
The code is available at \url{https://many-speech-analyses.github.io/suppl/simulations.html}, Section 2.\footnote{Cached model outputs can be found at \url{https://bit.ly/3AgdHAN}.}
Variability among teams was operationalized as the standard deviation of the teams' reported effects from \citet{silberzahn2018many} (which we \emph{z}-scored prior to simulations to make it comparable to our study).
For the mean of the teams' true standard deviation (0.68 \emph{z}-score), the simulation indicates that the degree of uncertainty around the estimated teams' standard deviation will be below 1 SD at any sample size greater than 10 teams.
Thus in order to achieve our main goal, i.e.~estimating variability among teams, we considered a minimum sample size of 10 teams as sufficient.
Given the exploratory nature of our study, however, we have sampled as many analysts as possible.
We received initial expression of interest to participate from more than 200 analysts, although there has been a substantial drop-out rate (see Section Results).

After submitting their analyses, we asked the analysts to also function as peer-reviewers.
Each team had to review four other analyses.
All analysts involved share co-authorship on this manuscript and participated in the collaborative process of producing the final manuscript.
Informed consent was obtained as part of the intake form.

@@

The analysis teams registered for participation and each of the analysts individually answered a demographic and expertise questionnaire (\texttt{intake\_form.pdf}).
A PDF version of this and all other questionnaires are available in the repository's \texttt{Questionnaires} component, at \url{https://bit.ly/3Cf3fdm}.
The questionnaire collected information on the analysts current position and self-estimated breadth and level of statistical expertise and acoustic analysis skills.
We then requested that they answer the question: \emph{Do speakers acoustically modify utterances to signal atypical word combinations?}
To do so, they were given the data generated by the experiment described in Section \protect\hyperlink{s:dataset}{The data set}.
The data included the audio recordings with corresponding time-aligned transcriptions in the form of Praat TextGrid files.
These can be found in the \texttt{Data} component at \url{https://bit.ly/3Ahawc7}.

Once their analysis was complete, they answered a structured questionnaire (\texttt{analytic\_quest.pdf}), providing information about their analysis technique, an explanation of their analytic choices, their quantitative results, and a statement describing their conclusions.
They also uploaded their analysis files (including the additionally derived data and text files that were used to extract and pre-process the acoustic data), their analysis code (if applicable), and a detailed journal-ready analysis section.

@@

Each analysis was evaluated by four different analysts teams who functioned as peer-reviewers.
Each peer-reviewer was randomly assigned to analyses from at least four analysis teams.
Reviewers evaluated the methods of each of their assigned analyses one at a time in a sequence determined by the initiating authors.
The sequences was systematically assigned so that, if possible, each analysis is allocated to each position in the sequence for at least one reviewer.

The process for a single reviewer was as follows.
First, the reviewer received a description of the methods of a single analysis.
This included the narrative methods section, the analysis team's answers to the questionnaire regarding their methods, including analysis code and the data set.
The reviewer was then asked in an online questionnaire (\texttt{peer\_review\_quest.pdf}) to rate both the acoustic and the statistical analyses and to provide an overall rating, using a scale of 0-100, respectively.
To help reviewers calibrate their rating, they were given the following guidelines:

@@

The reviewers were also given the option to include further comments in a text box for each of the three ratings.

After submitting the review, a methods section from a second analysis was then made available to the reviewer.
This same sequence was followed until all analyses allocated to a given reviewer were provided and reviewed.\footnote{We initially planned to simultaneously present all four (or more) methods sections to each reviewer after the fourth round, with the option to revise their original ratings and provide an explanation. We have decided to skip this last step due to time constrains.}
